Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands

### 2024-12-11 MANUSCRIPT.qmd
Update MANUSCRIPT.qmd

|              | Variable                  | Source       | Geoprocessing          |
|------------------|-------------------|------------------|------------------|
| Hydroclimate | Precipitation\*           | PRISM        | Basin average          |
|              | Mean Temperature\*        | PRISM        | Basin average          |
|              | Mean Evapotranspiration\* | TerraClimate | Basin average          |
| Geospatial   | Elevation\*               | DEM          | Basin average          |
|              | Area                      | DEM          | Basin average          |
|              | Slope                     | DEM          | Basin average          |
|              | Aspect                    | DEM          | Percent areal coverage |
|              | Land Cover\*              | NLCD         | Percent areal coverage |
|              | Hydrologic Soil Group\*   | SSURGO       | Percent areal coverage |
|              | Geology                   | USGS         | Percent areal coverage |
|              | Karst                     | USGS         | Percent areal coverage |

@@

Machine learning models can face issues with overfitting when provided with a large set of predicting features. This can cause reductions in performance on unseen data and requires greater computational power and memory storage [@feat_selec2017]. Dimensionality reduction is a powerful tool in addressing these issues which can be divided into two broad categories: feature extraction and feature selection. Feature extraction involves projecting the higher dimensional dataset to a feature space with less dimensions, though this entails creating a new set of features that lose the physical meaning of the original feature space. On the other hand, feature selection maintains a subset of the original features, all of which retain their physical meaning providing better readability and interpretability. Here, a supervised features selection was used to reduce the number of predictors and, as a result, increased learning performance, decreased computational costs, and reduced overfitting.

>>>>

|              | Variable                  | Source       | Geoprocessing          |
|--------------|---------------------------|--------------|------------------------|
| Hydroclimate | Precipitation\*           | PRISM        | Basin average          |
|              | Mean Temperature\*        | PRISM        | Basin average          |
|              | Mean Evapotranspiration\* | TerraClimate | Basin average          |
| Geospatial   | Elevation\*               | DEM          | Basin average          |
|              | Area                      | DEM          | Basin average          |
|              | Slope                     | DEM          | Basin average          |
|              | Aspect                    | DEM          | Percent areal coverage |
|              | Land Cover\*              | NLCD         | Percent areal coverage |
|              | Hydrologic Soil Group\*   | SSURGO       | Percent areal coverage |
|              | Geology                   | USGS         | Percent areal coverage |
|              | Karst                     | USGS         | Percent areal coverage |

@@

Machine learning models can face issues with overfitting when provided with a large set of predicting features. (CITATION) This can cause reductions in performance on unseen data and requires greater computational power and memory storage [@feat_selec2017]. Dimensionality reduction is a powerful tool in addressing these issues which can be divided into two broad categories: feature extraction and feature selection. Feature extraction involves projecting the higher dimensional dataset to a feature space with less dimensions, though this entails creating a new set of features that lose the physical meaning of the original feature space. On the other hand, feature selection maintains a subset of the original features, all of which retain their physical meaning providing better readability and interpretability. Here, a supervised features selection was used to reduce the number of predictors and, as a result, increased learning performance, decreased computational costs, and reduced overfitting.
